19Q2

### 2019-05-30 19Q2.Rmd
update Rmd

@@

g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
g2p_split <- split(g2p, g2p$biomarker_type_curated)
g2p_amp <- g2p_split[[1]]
g2p_expr <- g2p_split[[2]]
g2p_fus <- g2p_split[[3]]
g2p_fus$FusionPair <- sapply(X = g2p_fus$Feature.Names, function(x) strsplit(as.character(x)," ")[[1]][1])
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
g2p_mut <- g2p_split[[4]]
g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))
g2p_no_biomarker <- g2p_split[[4]]

@@

```{r fusion_calls, eval=TRUE}
fusions <- read.delim("./data_munging/19Q2/CCLE_fusions.csv.gz", header = TRUE, sep = ",")
fusions$LeftGene <- gsub(" .*", "", fusions$LeftGene)
fusions$RightGene <- gsub(" .*", "", fusions$RightGene)
fusions$X.FusionName <- gsub("--", "-", fusions$X.FusionName)
fusions <- select(fusions, DepMap_ID, X.FusionName, LeftGene, RightGene)
fusions <- as.data.frame(lapply(fusions, function(x) gsub("IGH@|IGH-@", "IGH", x)))
colnames(fusions) <- c("DepMap_ID", "FusionPair", "LeftGene", "RightGene")
fusions <- merge(fusions, ccl_meta, by = "DepMap_ID", all.x = TRUE)
fusions$G2P_Fusion <- ifelse(fusions$FusionPair %in% as.character(unique(g2p_fus$FusionPair)) | fusions$LeftGene %in% as.character(unique(g2p_fus$FusionPair)) | fusions$RightGene %in% as.character(unique(g2p_fus$FusionPair)), "Yes", "No")
fusions_filt <- unique(filter(fusions, G2P_Fusion == "Yes"))
```

@@

@@

ccle_fus <- auc %>% filter(Database == "CCLE") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
ccle_fus_grid <- expand.grid("DepMap_ID" = unique(ccle_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
ccle_fus <- merge(merge(ccle_fus, ccle_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
ccle_fus$G2P_Fusion <- ifelse(is.na(ccle_fus$G2P_Fusion), "No", as.character(ccle_fus$G2P_Fusion))

ctrp_fus <- auc %>% filter(Database == "CTRP") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
ctrp_fus_grid <- expand.grid("DepMap_ID" = unique(ctrp_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
ctrp_fus <- merge(merge(ctrp_fus, ctrp_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
ctrp_fus$G2P_Fusion <- ifelse(is.na(ctrp_fus$G2P_Fusion), "No", as.character(ctrp_fus$G2P_Fusion))

gdsc_fus <- auc %>% filter(Database == "GDSC") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
gdsc_fus_grid <- expand.grid("DepMap_ID" = unique(gdsc_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
gdsc_fus <- merge(merge(gdsc_fus, gdsc_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
gdsc_fus$G2P_Fusion <- ifelse(is.na(gdsc_fus$G2P_Fusion), "No", as.character(gdsc_fus$G2P_Fusion))

fus <- bind_rows(ccle_fus, ctrp_fus, gdsc_fus)
saveRDS(fus, "./data_munging/rds/fusions_merged.rds")
```

```{r}
fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
fus_summary <- fus %>% count(Drug, FusionPair, G2P_Fusion)
```

@@

# WILCOXON (MUT)

@@

WilcoxonTestDF <- function(dataframe, grouping, g2p_list, outfile) {
  require(ggpubr)
  if("Drug_Gene_Lin" %in% grouping) {
    # Filter out DGLs with too few samples in at least one mutation status category
    count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
    count_mut_category <- count_mut_n %>% count(Drug_Gene_Lin) %>% filter(n == 2)
    dgl_keep <- intersect(count_mut_n$Drug_Gene_Lin, count_mut_category$Drug_Gene_Lin)
    dataframe <- filter(dataframe, Drug_Gene_Lin %in% dgl_keep)
    dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
  }
  signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
  signif <- adj_signif(signif, alpha = 0.05)
  signif <- signif[order(signif$p),]
  if("Drug_Gene" %in% grouping) {
    signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No")
  }
  if("Drug_Gene_Lin" %in% grouping) {
    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No")
  }
  saveRDS(signif, outfile)
  return(signif)
}
```

@@

@@

```{r}
MakeMutHeatmap <- function(signif_g2p_dg, row_names, col_title, color, legend_title) {
  signif_grid <- dcast(signif_g2p_dg, Gene ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
  signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
  signif_grid <- signif_grid[complete.cases(signif_grid), ]
  signif_grid[signif_grid > 0.05] <- NA

  signif_grid_annot <- dcast(signif_g2p_dg, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
  signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
  signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
  signif_grid_annot[signif_grid_annot == "No"] <- ""
  signif_grid_annot[signif_grid_annot == "Yes"] <- "O"

  col_fun <- colorRamp2(c(0, 0.05), c(color, "gray97"))
  # Legend properties list
  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70",   at = seq(0, 0.05, by = 0.01), labels = seq(0, 0.05, by = 0.01))
  ht <- Heatmap(signif_grid,
                col = col_fun,
                na_col = "gray97",
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                  # annotation_height = max_text_width(colnames(signif_grid))),
                row_title = "Genes",
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "bottom",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
                  # if(signif_grid_annot[i, j] == "G") {
                  #   grid.circle(x = x, y = y, r = 0.02, gp = gpar(fill = "transparent", col = "black"))
                  # }
                }
                )
  return(ht)
}
```

```{r mut_heatmaps, eval=FALSE}
ht_ccle <- MakeMutHeatmap(signif_g2p_dg = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs")
png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

ht_ctrp <- MakeMutHeatmap(signif_g2p_dg = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "P-value", row_names = TRUE, color = "steelblue4", col_title = "Drugs")
png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeMutHeatmap(signif_g2p_dg = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "P-value", row_names = TRUE, color = "turquoise4", col_title = "Drugs")
png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()

ht_ccle2 <- MakeMutHeatmap(signif_g2p_dg = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "CCLE p-value                                                                               ", row_names = TRUE, color = "darkgreen", col_title = "")
ht_ctrp2 <- MakeMutHeatmap(signif_g2p_dg = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "CTRP p-value                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs")
ht_gdsc2 <- MakeMutHeatmap(signif_g2p_dg = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), legend_title = "GDSC p-value", row_names = FALSE, color = "turquoise4", col_title = "")
png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 10, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

# WILCOXON (Fusions)

>>>>

# Edit direction column
g2p <- add_column(g2p, Direction_Curated = NA, .after = "Direction")
g2p$Direction_Curated <-
  ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "sensitive|sensitivity||responsive")), "sensitivity",
         ifelse(!is.na(str_match(string = tolower(g2p$Direction), pattern = "resist")), "resistance", NA))

@@

g2p$biomarker_type_curated <- ifelse(is.na(g2p$biomarker_type_curated), "None", as.character(g2p$biomarker_type_curated))
g2p_split <- split(filter(g2p, !is.na(Drug)), g2p$biomarker_type_curated)
g2p_amp <- g2p_split[[1]]
g2p_expr <- g2p_split[[2]]
g2p_fus <- g2p_split[[3]]
g2p_fus$FusionPair <- sapply(X = g2p_fus$Feature.Names, function(x) strsplit(as.character(x)," ")[[1]][1])
g2p_fus$FusionPair <- ifelse(g2p_fus$FusionPair == "Fusions", as.character(g2p_fus$Gene), as.character(g2p_fus$FusionPair))
g2p_fus$Drug_FusionPair <- ifelse(is.na(g2p_fus$Drug) | is.na(g2p_fus$FusionPair), NA, paste0(g2p_fus$Drug, "_", g2p_fus$FusionPair))
g2p_mut <- g2p_split[[4]]
g2p_mut_genes <- unique(sapply(strsplit(as.character(g2p_mut$Drug_Gene)[!is.na(g2p_mut$Drug_Gene)], "_", fixed = TRUE), function(x) x[2]))
g2p_no_biomarker <- g2p_split[[5]]

@@

```{r fusion_calls, eval=TRUE}
fusions <- read.delim("./data_munging/19Q2/CCLE_fusions.csv.gz", header = TRUE, sep = ",")
fusions$LeftGene <- gsub(" .*", "", fusions$LeftGene)
fusions$RightGene <- gsub(" .*", "", fusions$RightGene)
fusions$X.FusionName <- gsub("--", "-", fusions$X.FusionName)
fusions <- select(fusions, DepMap_ID, X.FusionName, LeftGene, RightGene)
fusions <- as.data.frame(lapply(fusions, function(x) gsub("IGH@|IGH-@", "IGH", x)))
colnames(fusions) <- c("DepMap_ID", "FusionPair", "LeftGene", "RightGene")
fusions <- merge(fusions, ccl_meta, by = "DepMap_ID", all.x = TRUE)
```

@@

auc <- bind_rows(ccle_all, ctrp_all, gdsc_all) %>% drop_na(Drug_name)

@@

fusions_filt <- filter(fusions, FusionPair %in% unique(as.character(g2p_fus$FusionPair)))

ccle_fus <- auc %>% filter(Database == "CCLE") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
ccle_fus_grid <- expand.grid("DepMap_ID" = unique(ccle_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
ccle_fus <- merge(merge(ccle_fus, ccle_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
ccle_fus$Fusion_Status <- ifelse(!is.na(ccle_fus$LeftGene), "Yes", "No")
ccle_fus$Drug_FusionPair <- ifelse(is.na(ccle_fus$Drug) | is.na(ccle_fus$FusionPair), NA, paste0(ccle_fus$Drug, "_", ccle_fus$FusionPair))
ccle_fus$G2P_Drug_FusionPair <- ifelse(ccle_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
ccle_fus$G2P_Fusion <- ifelse(ccle_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
ccle_fus$Database <- "CCLE"

ctrp_fus <- auc %>% filter(Database == "CTRP") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
ctrp_fus_grid <- expand.grid("DepMap_ID" = unique(ctrp_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
ctrp_fus <- merge(merge(ctrp_fus, ctrp_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
ctrp_fus$Fusion_Status <- ifelse(!is.na(ctrp_fus$LeftGene), "Yes", "No")
ctrp_fus$Drug_FusionPair <- ifelse(is.na(ctrp_fus$Drug) | is.na(ctrp_fus$FusionPair), NA, paste0(ctrp_fus$Drug, "_", ctrp_fus$FusionPair))
ctrp_fus$G2P_Drug_FusionPair <- ifelse(ctrp_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
ctrp_fus$G2P_Fusion <- ifelse(ctrp_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
ctrp_fus$Database <- "CTRP"

gdsc_fus <- auc %>% filter(Database == "GDSC") %>% select(Cell_line, CCLE_histology, TCGA_classification, CCLE_name, DepMap_ID, Drug, AUC_IC50)
gdsc_fus_grid <- expand.grid("DepMap_ID" = unique(gdsc_fus$DepMap_ID), "FusionPair" = unique(fusions_filt$FusionPair))
gdsc_fus <- merge(merge(gdsc_fus, gdsc_fus_grid, by = "DepMap_ID", all = TRUE), fusions_filt, by = c("DepMap_ID", "CCLE_name", "CCLE_histology", "Cell_line", "FusionPair"), all = TRUE)
gdsc_fus$Fusion_Status <- ifelse(!is.na(gdsc_fus$LeftGene), "Yes", "No")
gdsc_fus$Drug_FusionPair <- ifelse(is.na(gdsc_fus$Drug) | is.na(gdsc_fus$FusionPair), NA, paste0(gdsc_fus$Drug, "_", gdsc_fus$FusionPair))
gdsc_fus$G2P_Drug_FusionPair <- ifelse(gdsc_fus$Drug_FusionPair %in% unique(as.character(g2p_fus$Drug_FusionPair)), "Yes", "No")
gdsc_fus$G2P_Fusion <- ifelse(gdsc_fus$FusionPair %in% unique(as.character(g2p_fus$FusionPair)), "Yes", "No")
gdsc_fus$Database <- "GDSC"

fus <- bind_rows(ccle_fus, ctrp_fus, gdsc_fus)
colnames(fus)[colnames(fus) == "AUC_IC50"] <- "Score"
saveRDS(fus, "./data_munging/rds/fusions_merged.rds")
```

```{r}
fus <- readRDS("./data_munging/rds/fusions_merged.rds") %>% drop_na(Drug)
fus_summary <- fus %>% count(Database, Drug, FusionPair, Fusion_Status)
```

@@

# WILCOXON TESTS

@@

WilcoxonTestDF <- function(dataframe, grouping, g2p_list, outfile) {
  require(ggpubr)
  if("Drug_Gene_Lin" %in% grouping) {
    # Filter out DGLs with too few samples in at least one mutation status category
    count_mut_n <- dataframe %>% count(Drug_Gene_Lin, Mutation) %>% filter(n >= 3)
    count_mut_category <- count_mut_n %>% count(Drug_Gene_Lin) %>% filter(n == 2)
    dgl_keep <- intersect(count_mut_n$Drug_Gene_Lin, count_mut_category$Drug_Gene_Lin)
    dataframe <- filter(dataframe, Drug_Gene_Lin %in% dgl_keep)
    dataframe$Drug_Gene_Lin <- as.character(dataframe$Drug_Gene_Lin)
    signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
    signif <- adj_signif(signif, alpha = 0.05)
    signif <- signif[order(signif$p),]
    signif$InG2P <- ifelse(signif$Drug_Gene_Lin %in% g2p_list, "Yes", "No")
  }
  if("FusionPair" %in% grouping) {
    # Filter out fusions with too few samples in at least one category
    count_n <- dataframe %>% count(Drug, FusionPair, Drug_FusionPair, Fusion_Status) %>% filter(n >= 3)
    count_category <- count_n %>% count(Drug, FusionPair, Drug_FusionPair) %>% filter(n == 2)
    keep <- intersect(count_n$Drug_FusionPair, count_category$Drug_FusionPair)
    dataframe <- filter(dataframe, Drug_FusionPair %in% keep)
    dataframe$Drug_FusionPair <- as.character(dataframe$Drug_FusionPair)
    signif <- compare_means(Score ~ Fusion_Status, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
    signif <- adj_signif(signif, alpha = 0.05)
    signif <- signif[order(signif$p),]
    signif$InG2P <- ifelse(signif$Drug_FusionPair %in% g2p_list, "Yes", "No")
  }
  if("Drug_Gene" %in% grouping) {
    signif <- compare_means(Score ~ Mutation, group.by = grouping, data = dataframe, paired = FALSE, method = "wilcox.test", p.adjust.method = "BH")
    signif <- adj_signif(signif, alpha = 0.05)
    signif <- signif[order(signif$p),]
    signif$InG2P <- ifelse(signif$Drug_Gene %in% g2p_list, "Yes", "No")
  }
  saveRDS(signif, outfile)
  return(signif)
}
```

## Mutation status

@@

## Fusions

```{r, eval=FALSE}
ccle_fus <- filter(fus, Database == "CCLE")
ccle_fus <- unfactorize(ccle_fus)
ccle_signif_fus <- WilcoxonTestDF(dataframe = ccle_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/ccle_signif_fusions.rds")

ctrp_fus <- filter(fus, Database == "CTRP")
ctrp_fus <- unfactorize(ctrp_fus)
ctrp_signif_fus <- WilcoxonTestDF(dataframe = ctrp_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/ctrp_signif_fusions.rds")

gdsc_fus <- filter(fus, Drug %in% g2p_drugs & Database == "GDSC")
gdsc_fus <- unfactorize(gdsc_fus)
gdsc_signif_fus <- WilcoxonTestDF(dataframe = gdsc_fus, grouping = c("FusionPair", "Drug", "Drug_FusionPair"), g2p_list = unique(as.character(g2p_fus$Drug_FusionPair[!is.na(g2p_fus$Drug_FusionPair)])), outfile = "./data_munging/rds/gdsc_signif_fusions.rds")
```

@@

```{r}
MakeWilcoxonHeatmap <- function(signif_df, feature, row_names, col_title, color, legend_title, row_title_txt) {
  if(!is.na(str_match(string = tolower(feature), pattern = "mut"))) {
    signif_grid <- dcast(signif_df, Gene ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
    signif_grid <- signif_grid[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid <- signif_grid[complete.cases(signif_grid), ]
    signif_grid[signif_grid > 0.05] <- NA

    signif_grid_annot <- dcast(signif_df, Gene ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-Gene)
    signif_grid_annot <- signif_grid_annot[g2p_gene_order, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
    signif_grid_annot[signif_grid_annot == "No"] <- ""
    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
  }
  if(!is.na(str_match(string = tolower(feature), pattern = "fus"))) {
    signif_grid <- dcast(signif_df, FusionPair ~ Drug, value.var = "p", fun.aggregate = mean, fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
    signif_grid <- signif_grid[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid <- signif_grid[complete.cases(signif_grid), ]
    signif_grid[signif_grid > 0.05] <- NA

    signif_grid_annot <- dcast(signif_df, FusionPair ~ Drug, value.var = "InG2P", fill = 0) %>% `rownames<-`(.[,1]) %>% select(-FusionPair)
    signif_grid_annot <- signif_grid_annot[, intersect(g2p_drug_order, colnames(signif_grid))]
    signif_grid_annot <- signif_grid_annot[complete.cases(signif_grid_annot), ]
    signif_grid_annot[signif_grid_annot == "No"] <- ""
    signif_grid_annot[signif_grid_annot == "Yes"] <- "O"
  }
  col_fun <- colorRamp2(c(0, 0.05), c(color, "gray97"))
  # Legend properties list
  ht_legend_list <- list(title = legend_title, title_position = "topleft", legend_direction = "horizontal", legend_width = unit(2, "in"), border = "gray70",   at = seq(0, 0.05, by = 0.01), labels = seq(0, 0.05, by = 0.01))
  ht <- Heatmap(signif_grid,
                col = col_fun,
                na_col = "gray97",
                rect_gp = gpar(col = "gray70"),
                heatmap_legend_param = ht_legend_list,
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                show_row_names = as.logical(row_names),
                row_names_side = "left",
                row_names_gp = gpar(fontsize = 10),
                column_names_side = "bottom",
                column_names_gp = gpar(fontsize = 10),
                show_column_names = FALSE,
                bottom_annotation = HeatmapAnnotation(
                  text = anno_text(colnames(signif_grid),
                                   rot = 45,
                                   gp = gpar(fontsize = 11),
                                   offset = unit(1, "npc"),
                                   just = "right"),
                  annotation_height = unit(0.85, "in")),
                  # annotation_height = max_text_width(colnames(signif_grid))),
                row_title = row_title_txt,
                row_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title = col_title, 
                column_title_gp = gpar(fontface = "bold", fontsize = 14),
                column_title_side = "bottom",
                cell_fun = function(j, i, x, y, width, height, fill) {
                  grid.text(signif_grid_annot[i, j], x, y, gp = gpar(fontsize = 20))
                  # if(signif_grid_annot[i, j] == "O") {
                  #   grid.circle(x = x, y = y, r = min(unit.c(width, height))*0.45, gp = gpar(fill = "transparent", col = "black"))
                  # }
                }
                )
  return(ht)
}
```

```{r mut_heatmaps, eval=FALSE}
ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Genes")
png(filename = "./plots/manuscript/ccle_mut_heatmap.png", width = 3, height = 10, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "P-value", row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
png(filename = "./plots/manuscript/ctrp_mut_heatmap.png", width = 9.5, height = 10, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "P-value", row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Genes")
png(filename = "./plots/manuscript/gdsc_mut_heatmap.png", width = 5, height = 10, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CCLE p-value                                                                               ", row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Genes")
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "CTRP p-value                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Genes")
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_g2p_dg, Gene %in% unique(g2p_mut$Gene)), feature = "mutation", legend_title = "GDSC p-value", row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Genes")
png(filename = "./plots/manuscript/drug_mut_heatmap.png", width = 13, height = 10, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```

```{r fus_heatmaps, eval=FALSE}
ht_ccle <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "P-value", row_names = TRUE, color = "darkgreen", col_title = "Drugs", row_title_txt = "Fusion Pairs")
png(filename = "./plots/manuscript/ccle_fus_heatmap.png", width = 2.5, height = 3, units = "in", res = 500)
draw(ht_ccle, heatmap_legend_side = "top")
dev.off()

ht_ctrp <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "P-value", row_names = TRUE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
png(filename = "./plots/manuscript/ctrp_fus_heatmap.png", width = 6, height = 3, units = "in", res = 500)
draw(ht_ctrp, heatmap_legend_side = "top")
dev.off()

ht_gdsc <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "P-value", row_names = TRUE, color = "turquoise4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
png(filename = "./plots/manuscript/gdsc_fus_heatmap.png", width = 5, height = 3, units = "in", res = 500)
draw(ht_gdsc, heatmap_legend_side = "top")
dev.off()

ht_ccle2 <- MakeWilcoxonHeatmap(signif_df = filter(ccle_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CCLE p-value                                                                               ", row_names = TRUE, color = "darkgreen", col_title = "", row_title_txt = "Fusion Pairs")
ht_ctrp2 <- MakeWilcoxonHeatmap(signif_df = filter(ctrp_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "CTRP p-value                                                                              ", row_names = FALSE, color = "steelblue4", col_title = "Drugs", row_title_txt = "Fusion Pairs")
ht_gdsc2 <- MakeWilcoxonHeatmap(signif_df = filter(gdsc_signif_fus, Drug %in% g2p_drugs), feature = "fusion", legend_title = "GDSC p-value", row_names = FALSE, color = "turquoise4", col_title = "", row_title_txt = "Fusion Pairs")
png(filename = "./plots/manuscript/drug_fus_heatmap.png", width = 13, height = 2.5, units = "in", res = 500)
draw(ht_ccle2 + ht_ctrp2 + ht_gdsc2, gap = unit(0.25, "in"), heatmap_legend_side = "top")
dev.off()
```
